Impact of Satellite Constellations on the Legacy Survey of Space and Time

### 2022-10-04 ms.tex
Updates from Overleaf

\begin{figure}[ht!]
% \plotone{plots/}
\caption{Example of satellite avoidance maps. \label{fig-simulated-scheduler}}
\end{figure}

@@

\begin{figure}[ht!]
%\includegraphics{}  % preferably .eps
\caption{Pixel loss vs coadded depth. \label{fig-trade-off}}
\end{figure}

>>>>

\begin{figure}[ht!]
\epsscale{0.3}
\plotone{plots/starlink_tles_v1_0.00_basisfunc.pdf}
\plotone{plots/starlink_tles_v2_0.00_basisfunc.pdf}
\plotone{plots/oneweb_tles_0.00_basisfunc.pdf}
\epsscale{1}
\caption{Example of satellite avoidance maps constructed for the scheduler. The maps have been rotated so zenith is in the center of the image. By varying the weight placed on these maps, the scheduler will more actively avoid regions of the sky where satellites could streak images. \label{fig-simulated-scheduler}}
\end{figure}

@@

\begin{figure}[ht!]
\epsscale{0.35}
\plotone{plots/slv1coadd.pdf}
\plotone{plots/slv2coadd.pdf}
\plotone{plots/onewcoadd.pdf}
\epsscale{1}
\caption{The trade off between pixels lost to streaks and final median coadded depth of the survey. Points to the right of the dashed line show improvement while those to the left signify the regained pixels do not adequatly compensate for the lost depth. In no situation are we able to prevent depth loss in at least some filters. \label{fig-trade-off}}
\end{figure}
